\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-25 paper/paper.tex
Reworking KM section

For the hard drive data we first estimate the empirical cdf for each model using the Kaplan-Meier estimator \cite{kaplan}.  With left truncation, however, the Kaplan-Meier estimate, $\widehat{F(t)_{KM}}$, is conditional based on hard drive $i$ surviving up to time $\tau_i^L$ where $L$ is the amount of time the hard drive was running before Backblaze starting monitoring the drive.  To get the unconditional distribution we correct the non-parametric estimates using a parametric adjustment outlined by Turnbull, and given in more detail by Meeker and Escobar \cite{turnbull,meeker}.  For each hard drive model we select $\tau_{\text{min}}^L$, the smallest left truncated time in the sample.  Then, using the parametric estimates of the parameters, we calculate $Pr(T>\tau_\text{min}^L)$ the probability a hard drive has survived up to $\tau_{\text{min}}^L$.  We then apply this correction to the non parametric estimates, which results in the unconditional distribution of time to failure.\\

>>>>

For the hard drive data we first estimate the empirical cdf for each model using the Kaplan-Meier estimator (KME)\cite{kaplan}.  With left truncation, however, the KME, which we denote by $\widehat{F(t)_{KM}}$, is conditional based on hard drive $i$ surviving up to time $\tau_i^L$ where $L$ is the amount of time the hard drive was running before Backblaze starting monitoring the drive.  To correct the non-parametric estimates, we adapt the adjustment method outlined by Turnbull, and given in more detail by Meeker and Escobar \cite{turnbull,meeker}.  For each hard drive model we select $t_{d,\text{min}}^L$, the smallest left truncated time in the sample.  Since $Pr(T>t_{d,\text{min}}^L)$, the probability a hard drive has survived up to $t_{d,\text{min}}^L$, is a function of the model parameters, by sampling from the full posterior distribution we can easily compute its posterior median, $\widehat{Pr_(T>t_{d,\text{min}}^L)}$. We use this to shift and rescale the KM thus  the unconditional distribution of time to failure, as in

$$\widehat{F(t)_{KMadj}} = .$$
